\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-12 paper/main.tex
pass on tool integration

\section{\tname: Database of Bugs in DL libraries}
\subsection{Bug Interface}

\begin{table}
  \centering
  \caption{\label{table:bug-interface}\tname's bug interface.}
\begin{tabular}{lp{6.5cm}}
\toprule
list-tests & List the tests available on this dataset\\
run-test & Runs one test\\
run-tests & Runs all the tests\\
show-info & Shows information about the tests available on this benchmark\\
stats & Shows statistics about this dataset (e.g., number of tests
that require GPU, number of tests that reproduce bugs in C or Python
code, etc.)\\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{table:bug-interface} shows \Fix{...}

\subsection{Test Oracle}

% \Fix{explain that the test passes if the bug can be reproduced}

The bug reproduction code includes python tests (pytest). The test oracle is satisfied when the bug is reproduced successfully. For bugs that throw an unexpected exception, the test catches the exception and reports the exception details along with a pass status. For bugs that result in incorrect output value, assertions are placed in the code to expect the incorrect output value, hence passing the test when the bug occurs. For bugs that crash after raising a signal, the code snippet is placed in a seperate file and executed, while the file contaning the actual test asserts the presence of the signal raised by the code. Upon successful reproduction, the original code crashes raising the proper signla and the assertion passes.

\subsection{Usage and Setup}

@@

Let's take the bug from issue no. 120903 from \torch. To make sure the framework is accessible system wide, the "framework" folder in the tool needs to be added to the PATH environment. The command to run a specific test is "run-test". To reproduce this bug, the command line prompt is as the following:

@@

The output will look like this upon reproducing successfully:

@@

In this output, the dependencies used in the reproduction of the bug are listed. Then, the pytest is executed and the exception (bug) is caught. Afterwards, the issue id is printed and the exception that has been caught is printed to demonstrate the bug. At the end, the test is shown to be passed, signifying the successful reproduction of the bug.

@@

To integrate a testing tool such as FreeFuzz, there are two steps:

1. A docker container with the environment of FreeFuzz
2. A script that takes the name of the library as an argument and run FreeFuzz on the library

To build a docker container for FreeFuzz, the following script can be run:

@@

>>>>

\textbf{Test Oracles.}~
The bug reproduction code includes python tests (pytest). The test
oracle is satisfied when the bug is reproduced successfully. For bugs
that throw an unexpected exception, the test catches the exception and
reports the exception details along with a pass status. For bugs that
result in incorrect output value, assertions are placed in the code to
expect the incorrect output value, hence passing the test when the bug
occurs. For bugs that crash after raising a signal, the code snippet
is placed in a seperate file and executed, while the file contaning
the actual test asserts the presence of the signal raised by the
code. Upon successful reproduction, the original code crashes raising
the proper signla and the assertion passes.\Fix{Please review and
  revise}

\textbf{Example}~\Fix{Can you show here the artifacts associated to bug
  120903 that you will use in the next section? If it takes too much
  space, show only directory with files and the test case.}

\section{\tname} % : Database of Bugs in DL libraries

This section presents the interface of \tname\ and walks the reader
through a demonstration showing the tool's functionality.

\subsection{Interface}

\begin{table}
  \centering
  \caption{\label{table:bug-interface}\tname's bug interface.}
\begin{tabular}{lp{6.5cm}}
  \toprule
  \textbf{command} & \textbf{description} \\
  \midrule
list-tests & List the tests available on this dataset\\
run-test & Runs one test\\
run-tests & Runs all the tests\\
run-tool & Runs a testing tool in a given buggy environment \\
show-info & Shows information about the tests available on this benchmark\\
stats & Shows statistics about this dataset (e.g., number of tests
that require GPU, number of tests that reproduce bugs in C or Python
code, etc.)\\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{table:bug-interface} shows the list of commands in the
\tname's interface along with a short description for these
commands. In the following we demonstrate \tname.
% \Fix{explain that the test passes if the bug can be reproduced}

\subsection{Usage}

To enable system-wide access of the framework, it is necessary to add
the directory \CodeIn{/framework} to the \CodeIn{PATH} environment
variable. Run the following commands for that:

\begin{lstlisting}[language=bash]
$> git clone git@github.com:ncsu-swat/bugsindlls.git
$> cd bugsindlls
$> export PATH=$PATH:`pwd`/framework
\end{lstlisting}

@@

Let us use the bug 120903~\Fix{cite} from \torch\ to demonstrate the
command \CodeIn{run-test}, which runs a test to reproduce a bug on an
environment with the necessary dependencies installed. Use the
following command to reproduce the bug:

@@

\noindent
Execution of this command produces the following output:

@@

The output shows the dependencies installed in the environment to
reproduce the bug and the verdict of the test oracle from pytest. In
this case, the execution of the bug-revealing test throws a runtime
error. Note that this test passes as it reproduces the intended bug.

%% Afterwards, the issue
%% id is printed and the exception that has been caught is printed to
%% demonstrate the bug. At the end, the test is shown to be passed,
%% signifying the successful reproduction of the bug.

%% \Fix{Please review and revise}

@@

Tool execution proceeds in two steps: (1) Creation of Docker container
associated with a tool and (2) Execution of the tool.  The following
script executes the first step, i.e., it builds a Docker container for
FreeFuzz:

% \Fix{walkthrough an example. Show input and part of output. Explain
%   the output.}
%% The user needs to execute two steps to integrate a testing tool (e.g.,
%% FreeFuzz) on \tname.
%% 1. Create a docker container for the tool
%% 2. A script that takes the name of the library as an argument and run FreeFuzz on the library

@@

\Fix{I am here -Marcelo}
